Analyses

### 2021-07-14 analyses.Rmd
- changed use time from min to h - added explanations to power analyses
- implemented major changes after feedback from reviewers

```{r results='hide'}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install

# define packages
packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
              "quanteda", "semTools", "tidyverse", "td")

@@

    # contrasts
    lik_ctrl = recode(version, "Control" = 0, "Like" = 1),
    lik_ctrl = na_if(lik_ctrl, "Like & Dislike"),
    likdis_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
    likdis_ctrl = na_if(likdis_ctrl, "Like"),
    likdis_lik = recode(version, "Like" = 0, "Like & Dislike" = 1),
    likdis_lik = na_if(likdis_lik, "Control"),
    likdislik_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
    likdislik_ctrl = na_if(likdislik_ctrl, "Like"),

@@

    # behavioral data
    words = replace_na(.$words, 0),
    self_dis = words + (reactions * 2),
    time_read_MIN = time_read / 60,
    time_sum_min_t2 = TIME_SUM_t2 / 60,

    # take logarithm
    posts_log = log1p(.$post_count),
    time_log = log1p(.$time_read), 
    posts_read_count_log = log1p(.$posts_read_count),
    words_log = log1p(.$words),
    self_dis_log = log1p(self_dis)
  )

# variable labels
var_names <- c("Privacy concerns", 
               "General gratifications", 
               "Specific gratifications",
               "Privacy deliberation", 
               "Self-efficacy", 
               "General trust", 
               "Specific trust",
               "Self-disclosure")

var_names_breaks <- c("Privacy\nconcerns", 
                      "General\ngratifications", 
                      "Specific\ngratifications",
                      "Privacy\ndeliberation", 
                      "Self-\nefficacy", 
                      "General\ntrust", 
                      "Specific\ntrust",
                      "Self-\ndisclosure")

@@

 1. ... concerns about what happens to my data.
 2. ... concerns about disclosing information about myself.
 3. ... no concerns.
 4. ... concerns that others could discover my real identity (i.e. my last and first name).
 5. ... concerns that information about myself could fall into wrong hands.
 6. ... concerns that others could discover what my political views are.
 7. ... concerns about my privacy.

@@

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

Shows that PC01_03 doesn't load well. As it's an inverted item that's not surprising. Also from a theoretic perspective it's suboptional, because it doesn't explicitly focus on privacy, but just concerns in general. Will be deleted.

@@

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "grats_general"
model <- "
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "grats_specific"
model <- "
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "pridel"
model <- "
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "trust_gen"
model <- "
trust =~ TR01_01 + a*TR01_05 + a*TR01_09
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

trust =~ trust_community + trust_provider + trust_system
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "trust_spec"
model <- "
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust =~ b*trust_community + b*trust_provider
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

 1. In principle, I felt able to write a comment.
 2. I felt technically competent enough to write a comment.
 3. In terms of the topic, I felt competent enough to express my opinion.
 4. I found it easy to express my opinion regarding the topic.
 5. I found it complicated to write a comment.
 6. I was overburdened to write a comment.

@@

```{r}
name <- "self-eff"
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "selfeff"
model <- "
self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ x*SE01_02
SE01_03 ~~ x*SE01_04
"
fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

@@

```{r}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  self_dis_lg =~ self_dis_log

  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"
fit_baseline <- sem(model_baseline, data = d, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

@@

```{r}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)

# combine d with d factor scores
d %<>% cbind(select(d_fs, -version, -self_dis_log))

@@

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-8, ], .) %>%
  set_rownames(var_names[-8])

@@

```{r fig.height=8, fig.width=8}
fig_fs_cor <- ggpairs(
  select(d_fs, -version),
  upper = list(continuous = "cor"),
  lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) +
  theme_bw()
print(fig_fs_cor)
```

@@

@@

```{r}
# create subset of data with all items that were used
d_sub <- d[, c("self_dis_log", "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", "TR01_02", "TR01_03", "TR01_04", "TR01_06", "TR01_07", "TR01_08", "TR01_10", "TR01_11", "TR01_12", "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", "SE01_01", "SE01_02", "SE01_03", "SE01_04", "male", "age", "edu")]

@@

In what follows we test for influential cases in baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.

```{r eval=T}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

@@

```{r eval=T}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

@@

```{r eval=T}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
```

@@

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
```

@@

We now use only variables, that is specific gratifications and privacy concerns.

@@

self_dis_log ~ a1*pri_con + b1*grats_spec

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
```

@@

# plot coeffs
fig_coeffs <- ggplot(d_coeffs, aes(x = b, y = Predictor)) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  facet_grid(~ Model) +
  guides(color = FALSE, shape = FALSE) + 
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12)) +
  coord_cartesian(xlim = c(-1.5, 1.5))

fig_coeffs
```

@@

The easiest way to assess the effect of the experimental manipulation on the variables is by visualizing their means. If 95% confidence intervals don't overlap, the variables differ significantly across the conditions. One can quickly see that there aren't any major effects.

```{r}
fig_fs_m <- ggplot(
  gather(d_fs, variable, value, -version) %>% 
    mutate(variable = factor(variable, levels = var_names_breaks)),
  aes(x = version, y = value, fill = version)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
  facet_wrap(~ variable, nrow = 2) + 
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12),
        legend.position="bottom",
        legend.title = element_blank()) +
  coord_cartesian(ylim = c(0, 7)) +
  scale_fill_brewer(palette="Greys")
fig_fs_m
```

>>>>

```{r results='hide'}
# install github packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install
# devtools::install_github("tdienlin/td")  # uncomment to install

# define packages
packages <- c("brms", "cowplot", "devtools", "faoutlier", "GGally", "gganimate",
              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
              "quanteda", "semTools", "tidyverse", "td")

@@

    # contrasts
    like = recode(version, "Control" = 0, "Like" = 1, "Like & Dislike" = 0),
    likedislike = recode(version, "Control" = 0, "Like" = 0, "Like & Dislike" = 1),
    control = recode(version, "Control" = 1, "Like" = 0, "Like & Dislike" = 0),
    lik_ctrl = recode(version, "Control" = 0, "Like" = 1),
    lik_ctrl = na_if(lik_ctrl, "Like & Dislike"),
    likdis_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
    likdis_ctrl = na_if(likdis_ctrl, "Like"),
    likdis_lik = recode(version, "Like" = 0, "Like & Dislike" = 1),
    likdis_lik = na_if(likdis_lik, "Control"),
    likdislik_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
    likdislik_ctrl = na_if(likdislik_ctrl, "Like"),

@@

    # behavioral data
    COMM = replace_na(.$words, 0),
    self_dis = words + (reactions * 2),
    time_read_MIN = time_read / 60,
    time_sum_min_t2 = TIME_SUM_t2 / 60,

    # take logarithm
    posts_log = log1p(.$post_count),
    time_log = log1p(.$time_read),
    posts_read_count_log = log1p(.$posts_read_count),
    words_log = log1p(.$words),
    COMM_log = log1p(COMM),
    self_dis_log = log1p(self_dis)
  )

# variable labels
var_names <- c("Privacy concerns", 
               "General gratifications", 
               "Specific gratifications",
               "Privacy deliberation", 
               "Self-efficacy", 
               "General trust", 
               "Specific trust",
               "Communication log")

var_names_breaks <- c("Privacy\nconcerns", 
                      "General\ngratifications", 
                      "Specific\ngratifications",
                      "Privacy\ndeliberation", 
                      "Self-\nefficacy", 
                      "General\ntrust", 
                      "Specific\ntrust",
                      "Communi-\ncation (log)")

@@

 1. ... concerns about what happens to my data.
 2. ... concerns about disclosing information about myself.
 3. ... no concerns. (reversed)
 4. ... concerns that others could discover my real identity (i.e. my last and first name).
 5. ... concerns that information about myself could fall into wrong hands.
 6. ... concerns that others could discover what my political views are.
 7. ... concerns about my privacy.

@@

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

Shows that PC01_03 doesn't load well. As it's an inverted item that's not surprising. Also from a theoretic perspective it's suboptimal, because it doesn't explicitly focus on privacy, but just concerns in general. Will be deleted.

@@

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "grats_general"
model <- "
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "grats_specific"
model <- "
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "pridel"
model <- "
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "trust_gen"
model <- "
trust =~ TR01_01 + a*TR01_05 + a*TR01_09
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

trust =~ trust_community + trust_provider + trust_system
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "trust_spec"
model <- "
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust =~ b*trust_community + b*trust_provider
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

 1. In principle, I felt able to write a comment.
 2. I felt technically competent enough to write a comment.
 3. In terms of the topic, I felt competent enough to express my opinion.
 4. I found it easy to express my opinion regarding the topic.
 5. I found it complicated to write a comment. (reversed)
 6. I was overburdened to write a comment. (reversed)

@@

```{r}
name <- "self-eff"
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

```{r}
name <- "selfeff"
model <- "
self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ x*SE01_02
SE01_03 ~~ x*SE01_04
"
fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
```

@@

## Communication
### Density plot

```{r}
ggplot(gather(select(d, COMM)), 
       mapping = aes(x = value)) +
  geom_density() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()
```

We see that Communication is severely skewed. Will hence be log-scaled for SEMs.

## Communication Logged

```{r}
ggplot(gather(select(d, COMM_log)), 
       mapping = aes(x = value)) +
  geom_density() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()
```

@@

```{r}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  comm_log =~ COMM_log

 comm_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"

fit_baseline <- lavaan::sem(model_baseline, data = d, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

@@

```{r}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, COMM_log)

# combine d with d factor scores
d %<>% cbind(select(d_fs, -version, -COMM_log))

# add centered predictors for interaction analyses later
d %<>%
  mutate(pri_con_fs_c = scale(pri_con_fs, scale = FALSE),
         grats_spec_fs_c = scale(grats_spec_fs, scale = FALSE),
         pri_del_fs_c = scale(pri_del_fs, scale = FALSE),
         trust_gen_fs_c = scale(trust_gen_fs, scale = FALSE),
         self_eff_fs_c = scale(self_eff_fs, scale = FALSE),
         con_x_del = pri_con_fs_c * pri_del_fs_c,
         grats_x_del = grats_spec_fs_c * pri_del_fs_c)

@@

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-c(8), ], .) %>%
  set_rownames(var_names[-c(8)])

@@

```{r fig.height=9, fig.width=9}
corr_plot <- ggpairs(select(d_fs, -version),
                     upper = list(continuous = cor_plot),
                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) + 
  theme_bw()
print(corr_plot)
ggsave("figures/results/cor_plot.png")
```

@@

In what follows, we report power analyses for our study. Please note that we conduct a rudimentary power-analysis, assuming bivariate correlations. To explain, at the time we were not yet aware of the existence of power analyses for multivariate structural equation models.

@@

```{r}
# create subset of data with all items that were used
d_sub <- d[, c("COMM", "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", "TR01_02", "TR01_03", "TR01_04", "TR01_06", "TR01_07", "TR01_08", "TR01_10", "TR01_11", "TR01_12", "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", "SE01_01", "SE01_02", "SE01_03", "SE01_04", "male", "age", "edu")]

@@

[Note: These lines stopped working after some time, potentially due to changes in package.]

In what follows we test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.

```{r eval=F}
cooks_dis <- gCD(d, model_baseline)
plot(cooks_dis)
```

@@

```{r eval=F}
infl_cases <- invisible(rownames(print(cooks_dis)))
```

@@

```{r eval=F}
infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
d %>% 
  filter(case_token %in% infl_cases_tokens) %>% 
  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
  kable() %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```

@@

COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
COMM_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_prereg <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
```

Results show that there's only one significant predictor of Communication, being self-efficacy. The other predictors are in the direction as planned, albeit not significant. Trust, however, shows the inverse relation as effect, that is, more trust, less communication.

@@

COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_adapted <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
```

Effects become a bit larger and significant, which seems to make sense. However, this also includes trust, which is a significant negative predictor of communication.

### Model "Interaction"

We now estimate an interaction model, as suggested by an anomymous reviewer. To estimate the interaction we'll use factor scores.

```{r}
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

COMM_log ~ a1*pri_con_fs_c + b1*grats_spec_fs_c + c1*pri_del_fs_c + con_x_del + grats_x_del + d1*self_eff + e1*trust_gen

# Covariates
COMM_log + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 + pri_con_fs_c + grats_spec_fs_c + pri_del_fs_c + con_x_del ~ male + age + edu

# Covariances
pri_con_fs_c ~~ grats_spec_fs_c + pri_del_fs_c + con_x_del + grats_x_del + self_eff + trust_gen
grats_spec_fs_c ~~ pri_del_fs_c + con_x_del + grats_x_del + self_eff + trust_gen
pri_del_fs_c ~~ con_x_del + grats_x_del + self_eff + trust_gen
con_x_del ~~ grats_x_del + self_eff + trust_gen
grats_x_del ~~ self_eff + trust_gen
self_eff ~~ trust_gen
male ~~ age + edu
age ~~ edu
"

fit_inter <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_inter, fit = TRUE, std = TRUE)
rsquare_fit_inter <- inspect(fit_inter, what = "rsquare")["comm"]
```

Results are interesting. Both interaction effects are significant. If Deliberation increases, the effect of concerns on communication increase (net effect). If Deliberation increases, the effect of gratifications on communication decrease. Hence, could imply that if people think more, concerns more relevant than benefits.

@@

We now use only two variables, namely specific gratifications and privacy concerns.

@@

COMM_log ~ a1*pri_con + b1*grats_spec

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu

# Covariances
male ~~ age + edu
age ~~ edu
"
fit_simple <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
```

Works as hypothesized.

@@

# plot coeffs
fig_coeffs <- ggplot(d_coeffs, aes(x = b, y = Predictor)) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  facet_grid(~ Model) +
  guides(color = FALSE, shape = FALSE) + 
  theme_bw() +
  theme(axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12)) +
  coord_cartesian(xlim = c(-1.3, 1.3))
ggsave("figures/results/coeffs.png")
fig_coeffs
```

### Model "BRMS"

Because the dependent variable is a zero-inflated Poisson distribution, we'll also run Bayesian models, which can explicitly account for this distribution.

#### Adapted Model

```{r}
fit_brms <- brm(COMM ~ pri_con_fs + grats_spec_fs + pri_del_fs + self_eff_fs + trust_gen_fs, data = d, family = zero_inflated_poisson())
d_predicted <- predict(fit_brms) %>% as.data.frame()
summary(fit_brms)
```

Shows very similar results compared to SEM. Again, trust a negative predictor.

##### Plot predicted values

Let's also look at how values are predicted to see how model performs.

```{r}
d_predicted <- predict(fit_brms) %>% as.data.frame()
ggplot(d_predicted, aes(Estimate)) + 
  geom_density()
```

Let's also plot actual values.

```{r}
# plot actual values
ggplot(d, aes(COMM)) + 
  geom_density()
```

Model-predicted values don't closely match actual values.

#### Without Trust

Because trust has a negative coefficient, which seems generally implausible, we also run a model without trust.

```{r}
fit_brms <- brm(COMM ~ pri_con_fs + grats_spec_fs + pri_del_fs + self_eff_fs, data = d, family = zero_inflated_poisson())
d_predicted <- predict(fit_brms) %>% as.data.frame()
summary(fit_brms)
```

Seems to make sense. Self-Efficacy a strong predictor of behavior.

#### Simple model

```{r}
fit_brms_simple <- brm(COMM ~ pri_con_fs + grats_spec_fs, data = d, family = zero_inflated_poisson())
summary(fit_brms_simple)
```

Also works, showing somewhat stronger effects.

#### Simple hurdle model

```{r}
fit_brms_simple_hurdle <- brm(bf(COMM ~ pri_con_fs + grats_spec_fs, hu ~ pri_con_fs + grats_spec_fs), data = d, family = hurdle_poisson())
summary(fit_brms_simple_hurdle)
```

Results don't differ markedly.

#### Interaction model

```{r}
fit_brms <- brm(COMM ~ pri_con_fs_c * grats_spec_fs_c, data = d, family = zero_inflated_poisson())
summary(fit_brms)
```

The effect of concerns on communication become weaker if gratifications increase.

#### Interaction model including deliberation

```{r}
fit_brms <- brm(COMM ~ pri_con_fs_c * grats_spec_fs_c + pri_con_fs_c * pri_del_fs_c + grats_spec_fs_c * pri_del_fs_c, data = d, family = zero_inflated_poisson())
summary(fit_brms)
```

@@

The easiest way to assess the effect of the experimental manipulation on the variables is by visualizing their means. If 83% confidence intervals don't overlap, the variables differ significantly across the conditions. One can quickly see that there aren't any major effects.
